Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2023-02-02 write-up/fda-recurrent.tex
updating paper first, then code for revision

@@

@@

A concern with the proposed approach is the selection of window-length, $\Delta$.  Here we investigate the impact of misspecification of the window length for $\beta(t) = \beta_1 \cdot \sin \left( 2 \pi s / \Delta - \pi /2 \right)$ and the true window length ($\Delta^\star$) is set to 32-minutes.  See Appendix~\ref{app:delta} for a similar discussion for $\beta(t) = \beta_0 \exp \left( - \beta_1 s \right)$.  As in the previous simulation, we generate 1000 datasets per condition each consisting of 500 user-days.  For each simulation, we analyze the data using window lengths $\Delta \in (26,29,32,35,37)$.

@@

@@

In Appendix~\ref{app:csmissing}, Figures~\ref{fig:missing_eda} and~\ref{fig:missing_acc} present the per-patient average fraction with missing EDA and AI in 30-minute windows respectively. For EDA, we have a wide range of missingness -- from $0\%$ to over $40$\% across individuals with most between $5\%$ and $30\%$ average fraction missing.  For AI, the missingness is less pronounced -- from $0\%$ to $15\%$ across individuals with most between $0\%$ and $10\%$ average fraction missing.  To assess the impact of missing data, we perform the imputation under uncongeniality using the boostrap and multiple imputation strategy described in Section~\ref{section:miuncong}.  Here we see that the EDA curve remains non-significant while the region where the AI curve is significant widens slightly to be the prior 4 minutes.

@@

\newpage
\appendix

\section{Derivation of the design-unbiased score equations}

\begin{proof}[Proof of Lemma~\ref{lemma:logistic}]
Recall~$\frac{d}{d\theta} \log h_i (t; \theta) = \frac{h^{(1)}_i (t; \theta)}{h_i (t; \theta)}$. Under the log-linear intensity function given by~\eqref{eq:approx_hazard}, $\frac{d}{d\theta} \log h_i (t; \theta) = W_{i,t}$ and
\[
\frac{d}{d \theta} \log \left( \pi_i (t) + h_i (t;\theta) \right) =
\frac{\exp \left( W_{i,t}^\top \theta \right)}{\pi_i (t) + \exp
  \left( W_{i,t}^\top \theta \right)} W_{i,t}
\]
Therefore,
\begin{align*}
\tilde U_n (\theta)
  &= \sum_{i=1}^n \left \{ \sum_{t \in \bfT_i} W_{i,t} - \sum_{t \in \bfT_i \cup \bfD_i} \frac{\exp \left( W_{i,t}^\top \theta \right)}{\pi_i (t) + \exp \left( W_{i,t}^\top \theta \right)}  W_{i,t} \right \} \\
  &= \sum_{i=1}^n \left \{ \sum_{t \in \bfT_i} \frac{\pi_i (t)}{\pi_i (t) + \exp \left( W_{i,t}^\top \theta \right)} W_{i,t} - \sum_{t \in \bfD_i} \frac{\exp \left( W_{i,t}^\top \theta \right)}{\pi_i (t) + \exp \left( W_{i,t}^\top \theta \right)} W_{i,t} \right \} \\
  &= \sum_{i=1}^n \left \{ \sum_{t \in \bfT_i} w_{i} (t; \theta) W_{i,t} -
    \sum_{t \in D_i} (1 - w_i (t; \theta)) W_{i,t} \right \} \\
  &= - \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i} \left[ {\bf 1} [t \in \bfD_i]  - w_{i} (t; \theta) \right] W_{i,t} \\
  &= \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
    \left[ {\bf 1} [t \in \bfD_i]  - \frac{1}{1 + \exp\left( - (
          \tilde W_{i,t}^\top \theta + \log (\pi_i (t) ) ) \right)}
    \right] \tilde W_{i,t}.
\end{align*}
where~$\tilde W_{i,t} = - W_{i,t}$. This is exactly the score equation
for logistic regression with offset~$\log \pi_i (t)$.
\end{proof}

\begin{proof}[Proof of Lemma~\ref{lemma:simpleasym}]
% Lemma~\ref{lemma:simpleasym} will be proven under regularity conditions A-E in~\cite[pp. 420--421]{Andersen1993} along with the following assumptions related to the subsampling rate~$\pi_i (t)$.
Define the joint counting process
\[
M_i (t) = N_i (t) - \int_0^t (h_i (s; \theta) + \pi_i (s)) R_i (s) ds.
\]
where~$N_i (t)$ is the counting process with jumps at all~$t \in \bfT_i \cup \bfD_i$. Asymptotic consistency is guaranteed~\cite[Theorem VI.1.1]{Andersen1993} if
\begin{equation}
\label{eq:andersen1}
n^{-1} \tilde U_n (\theta_0 ) \overset{P}{\to} 0,
\end{equation}
and
\begin{equation}
\label{eq:andersen2}
n^{-1} \frac{d}{d \theta^{\top}} \tilde U_n (\theta) \big |_{\theta =
  \theta_0} = \Xi (\theta),
\end{equation}
and
\begin{equation}
\label{eq:andersen3}
\lim_{n \to \infty} P \left( \left | n^{-1} \frac{d^2}{d \theta_j d
      \theta_k} \tilde U_n (\theta) \right | < M \text{ for all }
  j,k \text{ and all } \theta \in \Theta_0 \right) = 1
\end{equation}
To prove~\eqref{eq:andersen1}, we decompose~$\tilde U_n (\theta_0)$ into
three terms
\begin{equation}
\label{eq:decomp}
n^{-1} \tilde U_n (\theta_0) = n^{-1} U_n (\theta_0 )  + n^{-1} \left(
  \hat U_n (\theta_0) - U_n (\theta) \right) + n^{-1} \left(\tilde U_n
  (\theta_0) - \hat U_n (\theta_0) \right)
\end{equation}
where, recall,~$\hat U_n (\theta_0)$ are the logistic score equations with $\int_0^\infty X_i(t,s) \beta(s) ds$ and~$\tilde U_n (\theta_0)$ with the approximation~$C_{i,t}^\top J_{\phi, \psi} {\bf b}$. \cite{Andersen1993} (Theorem VI.1.1) show that~$n^{-1} U_n (\theta_0)
\to 0$. The second term
\begin{align*}
n^{-1} \left( \hat U_n (\theta_0) - U_n (\theta_0) \right) =
  \frac{1}{n} \sum_{i=1}^n \int_0^{\tau} \frac{h^{(1)} (s;
  \theta_0)}{\pi_i (s) + h (s;\theta_0)} d M_i (s).
\end{align*}
where~$h(\cdot; \theta_0)$ is given by~\eqref{eq:hazardlinear}. Lenglart's inequality implies the second term converges in probability to zero under Assumptions~\ref{E1} and~\ref{E2}. The third term satisfies
\begin{align*}
  &n^{-1} \left \| \hat U_n (\theta_0) - \tilde U_n (\theta_0) \right \| \\
  \leq & M n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i} \bigg \| g
         \left( \tilde W_{i,t}^\top \theta  + \sum_{k=K_x+1}^\infty \hat
         c_{i,k} (t) \int_{t-\Delta}^t \hat \psi_k (s) \phi (s)^\top b
         + \log (\pi_i (t) ) \right) - g \left( \tilde W_{i,t}^\top
         \theta + \log (\pi_i (t)) \right) \bigg \| \\
&\leq M n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
    \sup_{x \in \mathbb{R}} \left \| g^\prime \left( x \right)
  \right\| \times \left \| \sum_{k=K_x+1}^\infty \hat c_{i,k} (t)
  \sum_{l=1}^{K_b} \int_{t-\Delta}^t \hat \psi_k (s) \phi_l (s) b_l
  \right \| \\
&= \frac{M}{4} n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
  \sum_{l=1}^{K_b} \left \| \int_{t-\Delta}^t
  \left( X(t,s) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \right)
  \phi_l (s) b_l\right \| \\
&\to \frac{M}{4} \int_0^\tau \sum_{l=1}^{K_b} \left \| \int_{t-\Delta}^t
  \left( X(t,s) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \right)
  \phi_l (s) b_l\right \| (f_0(t) + f_1(t)) dt
\end{align*}
where~$M = \sup \| \tilde W_{i,t} \|$,~$g(x) = 1/(1+\exp(-x))$ is the
expit function.
The second inequality is due to the Taylor remainder theorem. The third is due to~$g^\prime (x) = e^x/(1+e^x)^2 \leq e^0/(1+e^0)^2 = 1/4$, reordering the summation, and rewriting the error term in terms of the difference between~$X(t,s)$ and the approximation with truncation level~$K_x$. Letting~$n \to \infty$ allows us to re-write the outside sums in terms of the integrated difference where the integral is with respect to the joint event and sampling distributions~$(f_0(t) + f_1 (t))$. Finally, under Assumptions~\ref{assumption:truncation}, \cite{Park2018} show
\[
X(t,s) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \overset{P}{\to} 0
\]
as~$K_x \to \infty$, which implies the third term goes to zero as the truncation level goes to infinity. The same argument can be used in conjunction under assumptions~\ref{E1} and~\ref{E4} to prove~\eqref{eq:andersen2}.

To prove~\eqref{eq:andersen3}, we start with equation~\eqref{eq:approxscore}, which we rewrite here for completeness:
\[
\hat{U}_n (\theta) = \sum_{i=1}^n \left[ \sum_{u \in \bfT_i} w_i(u; \theta)
  \frac{h^{(1)} (u; \theta)}{ h ( u; \theta)}  - \sum_{u \in \bfD_i} w_i(u;
  \theta) \frac{h_i^{(1)} (u; \theta)}{ \pi_i (u) } \right].
\]
Let~$N_i^{(e)} (t)$ and $N_i^{(s)} (t)$ be the event and subsampling counting processes with jumps at $t \in \bfT_i$ and $\bfD_i$ respectively.  Then
\begin{equation}
\label{eqapp:upperbound}
\left | n^{-1} \frac{d^2}{d \theta_j d \theta_k} \tilde U_n (\theta)  \right | \leq \frac{1}{n} \sum_{i=1}^n \int_0^\tau w_i (t;\theta) \times H_{in} (t) R_i (t) dN_i^{(e)} (t) +
\frac{1}{n} \sum_{i=1}^n \int_0^\tau \frac{w_i (t;\theta)}{\pi_i (t)} \times G_{in} (t) R_i (t) dN_i^{(e)} (t)
\end{equation}
where $H_{in}(t)$ and $G_{in}(t)$ are from Condition VI.1.1(E) in~\cite[pp. 421]{Andersen1993}. The first term converges in probability to a finite quantity by~\cite{Andersen1993}.  Since~$w_i(t;\theta)/\pi_i (t) = (\pi_i(t)+h_i(t;\theta))^{-1}$, the second term which simplifies to
\[
\frac{1}{n} \sum_{i=1}^n \int_0^\tau \frac{G_{in} (t)}{\pi_i (t)+h_i(t;\theta)} R_i(t) dN_i^{(e)} (t)
\leq
\frac{1}{L \cdot n} \sum_{i=1}^n \int_0^\tau G_{in} (t) R_i (t) dN_i^{(e)} (t)
\]
by Assumption~\ref{E1} (i.e., the subsampling rate is lower bounded by $L$). The right hand side is the optional variation of the local square integrable martingale
$$
\frac{1}{L \cdot n} \sum_{i=1}^n \int_0^t G^{1/2}_{in} (s) dN_i^{(e)} (s)
$$
This martingale has predicable variation process
$$
\frac{1}{L \cdot n} \sum_{i=1}^n \int_0^t G_{in} (s) \pi_i (s) R_i (s) ds
$$
Since both processes have the same limits, conditions VI.1.1(E) in~\cite{Andersen1993} and Assumption~\ref{E1} imply that the second term on the right hand side of~\eqref{eqapp:upperbound} also converges to a finite quantity as $n \to \infty$ for every $K_x$ which completes the proof.

This proves~$\hat \theta_n \overset{P}{\to} \theta_0$ as $n \to \infty$ and $K_x \to \infty$. Note that the argument holds for any choice of weight functions~$w_i (t;\theta)$; implying convergence holds more broadly for all approximate score equations in~\eqref{eq:approxscore}.
\end{proof}

\begin{proof}[Proof of Asymptotic Normality]
Consider a Taylor-expansion of $\tilde U_n (\theta)$ centered at $\theta_0$ when $\hat \theta_n \in \Theta_0$.  We can write as
\begin{align*}
\tilde U_n (\hat \theta_n) &= \tilde U_n (\theta_0) -  (\hat \theta_n - \theta_0) \frac{\partial}{\partial \theta} \tilde U_n (\theta) \mid_{\theta=\theta_0} - (\hat \theta_n - \theta_0) \sum_{l=1}^p (\hat \theta_{ln} - \theta_{l0}) \frac{\partial^2}{\partial \theta \partial \theta_l} \tilde U_n (\theta) \mid_{\theta=\theta^\star} \\
0 &= \tilde U_n (\theta_0) + (\hat \theta_n - \theta_0) \left[ \frac{\partial}{\partial \theta} \tilde U_n (\theta) \mid_{\theta=\theta_0} + \frac{1}{2} \sum_{l=1}^p (\hat \theta_{ln} - \theta_{l0}) \frac{\partial^2}{\partial \theta \partial \theta_l} \tilde U_n (\theta) \mid_{\theta=\theta^\star} \right] \\
n^{1/2} (\hat \theta_n - \theta_0) &= \left[ \frac{1}{n} \frac{\partial}{\partial \theta} \tilde U_n (\theta) \mid_{\theta=\theta_0} + \frac{1}{2n} \sum_{l=1}^p (\hat \theta_{ln} - \theta_{l0}) \frac{\partial^2}{\partial \theta \partial \theta_l} \tilde U_n (\theta) \mid_{\theta=\theta^\star} \right]^{-1} n^{-1/2} \tilde U_n (\theta_0)
\end{align*}
where~$\theta^\star$ is on the line segment between $\hat \theta_n$ and $\theta_0$. First, the term
$$
\frac{1}{n} \frac{\partial}{\partial \theta} \tilde U_n (\theta) \mid_{\theta=\theta_0} + \frac{1}{2n} \sum_{l=1}^p (\hat \theta_{ln} - \theta_{l0}) \frac{\partial^2}{\partial \theta \partial \theta_l} \tilde U_n (\theta) \mid_{\theta=\theta^\star}
\overset{P}{\to} \Xi(\theta_0)
$$
under conditions VI.1.1(A)--(E) in~\cite{Andersen1993} and Assumptions~\ref{E1}--\ref{E4}.  To see this, note the first term converges to $\Xi(\theta_0)$ while the second term is bounded in probability by $p M \| \theta^\star - \theta_0 \|$ for some finite constant~$M$ independent of~$\theta^\star$ where $\| \cdot \|$ is the Euclidean norm.  The second term therefore goes to zero since $\| \theta^\star - \theta_0 \| \to 0$ as $n \to \infty$.

We now consider $n^{-1/2} \tilde U_n (\theta_0 )$. Recall $\tilde U_n (\theta_0)$ can be decomposed into three terms as in~\eqref{eq:decomp}. Here, we assume $K_x \to \infty$ so the final term is negligible.  This leaves two terms
$$
U_n (\theta_0) = \sum_{i=1}^n \int_0^\tau \frac{h^{(1)}(u; \theta)}{h (u;\theta)} dM_i^{(e)} (t)
$$
where~$N_i^{(e)} (t)$ and $N_i^{(s)} (t)$ are the orthogonal event and subsampling counting processes with jumps at times $t \in \bfT_i$ and $t \in \bfD_i$ respectively.
and
\begin{align*}
(\hat U_n (\theta_0) - U_n (\theta_0) )
&= \sum_{i=1}^n \int_0^\tau \frac{h^{(1)}(s; \theta_0)}{\pi_i (s) + h(s; \theta_0)} dM_i (s) \\
&= \sum_{i=1}^n \int_0^\tau \frac{h^{(1)}(s; \theta_0)}{\pi_i (s) + h(s; \theta_0)} dM^{(e)}_i (s) +
\sum_{i=1}^n \int_0^\tau \frac{h^{(1)}(s; \theta_0)}{\pi_i (s) + h(s; \theta_0)} dM_i^{(s)} (s) \\
&= \sum_{i=1}^n \int_0^\tau (1-w(s;\theta_0)) \cdot \frac{h^{(1)}(s; \theta_0)}{h_i (s;\theta_0)} dM_i^{(e)} (s) +
\sum_{i=1}^n \int_0^\tau w(s;\theta_0) \cdot \frac{h^{(1)}(s; \theta_0)}{\pi_i (s)} dM_i^{(s)} (s)
\end{align*}
Taking difference with $U_n(\theta_0)$, the first term becomes
\[
\sum_{i=1}^n \int_0^\tau w(s;\theta_0) \cdot \frac{h^{(1)}(s; \theta_0)}{h_i (s;\theta_0)} dM_i^{(e)} (s)
\]

>>>>

\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}% latexmk will find this if $recorder=0 (however, in that case, it will ignore #1 if it is a .aux or .pdf file etc and it exists! if it doesn't exist, it will appear in the list of dependents regardless)
  \@addtofilelist{#1}% if you want it to appear in \listfiles, not really necessary and latexmk doesn't use this
  \IfFileExists{#1}{}{\typeout{No file #1.}}% latexmk will find this message if #1 doesn't exist (yet)
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}
%%% END HELPER CODE

% put all the external documents here!
\myexternaldocument{fda-recurrent-supplement}

@@

\subsection{Related work}

@@

A concern with the proposed approach is the selection of window-length, $\Delta$.  Here we investigate the impact of misspecification of the window length for $\beta(t) = \beta_1 \cdot \sin \left( 2 \pi s / \Delta - \pi /2 \right)$ and the true window length ($\Delta^\star$) is set to 32-minutes.  See Section~\ref{app:delta} of the supplementary materials for a similar discussion for $\beta(t) = \beta_0 \exp \left( - \beta_1 s \right)$.  As in the previous simulation, we generate 1000 datasets per condition each consisting of 500 user-days.  For each simulation, we analyze the data using window lengths $\Delta \in (26,29,32,35,37)$.

@@

\subsection{Comparison to alternative methods} \label{section:simcomparisons}

@@

In Section~\ref{app:csmissing} of the supplementary materials, Figures~\ref{fig:missing_eda} and~\ref{fig:missing_acc} present the per-patient average fraction with missing EDA and AI in 30-minute windows respectively. For EDA, we have a wide range of missingness -- from $0\%$ to over $40$\% across individuals with most between $5\%$ and $30\%$ average fraction missing.  For AI, the missingness is less pronounced -- from $0\%$ to $15\%$ across individuals with most between $0\%$ and $10\%$ average fraction missing.  To assess the impact of missing data, we perform the imputation under uncongeniality using the boostrap and multiple imputation strategy described in Section~\ref{section:miuncong}.  Here we see that the EDA curve remains non-significant while the region where the AI curve is significant widens slightly to be the prior 4 minutes.

@@

% \newpage
% \appendix

% \section{Derivation of the design-unbiased score equations}

% \begin{proof}[Proof of Lemma~\ref{lemma:logistic}]
% Recall~$\frac{d}{d\theta} \log h_i (t; \theta) = \frac{h^{(1)}_i (t; \theta)}{h_i (t; \theta)}$. Under the log-linear intensity function given by~\eqref{eq:approx_hazard}, $\frac{d}{d\theta} \log h_i (t; \theta) = W_{i,t}$ and
% \[
% \frac{d}{d \theta} \log \left( \pi_i (t) + h_i (t;\theta) \right) =
% \frac{\exp \left( W_{i,t}^\top \theta \right)}{\pi_i (t) + \exp
%   \left( W_{i,t}^\top \theta \right)} W_{i,t}
% \]
% Therefore,
% \begin{align*}
% \tilde U_n (\theta)
%   &= \sum_{i=1}^n \left \{ \sum_{t \in \bfT_i} W_{i,t} - \sum_{t \in \bfT_i \cup \bfD_i} \frac{\exp \left( W_{i,t}^\top \theta \right)}{\pi_i (t) + \exp \left( W_{i,t}^\top \theta \right)}  W_{i,t} \right \} \\
%   &= \sum_{i=1}^n \left \{ \sum_{t \in \bfT_i} \frac{\pi_i (t)}{\pi_i (t) + \exp \left( W_{i,t}^\top \theta \right)} W_{i,t} - \sum_{t \in \bfD_i} \frac{\exp \left( W_{i,t}^\top \theta \right)}{\pi_i (t) + \exp \left( W_{i,t}^\top \theta \right)} W_{i,t} \right \} \\
%   &= \sum_{i=1}^n \left \{ \sum_{t \in \bfT_i} w_{i} (t; \theta) W_{i,t} -
%     \sum_{t \in D_i} (1 - w_i (t; \theta)) W_{i,t} \right \} \\
%   &= - \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i} \left[ {\bf 1} [t \in \bfD_i]  - w_{i} (t; \theta) \right] W_{i,t} \\
%   &= \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
%     \left[ {\bf 1} [t \in \bfD_i]  - \frac{1}{1 + \exp\left( - (
%           \tilde W_{i,t}^\top \theta + \log (\pi_i (t) ) ) \right)}
%     \right] \tilde W_{i,t}.
% \end{align*}
% where~$\tilde W_{i,t} = - W_{i,t}$. This is exactly the score equation
% for logistic regression with offset~$\log \pi_i (t)$.
% \end{proof}

% \begin{proof}[Proof of Lemma~\ref{lemma:simpleasym}]
% % Lemma~\ref{lemma:simpleasym} will be proven under regularity conditions A-E in~\cite[pp. 420--421]{Andersen1993} along with the following assumptions related to the subsampling rate~$\pi_i (t)$.
% Define the joint counting process
% \[
% M_i (t) = N_i (t) - \int_0^t (h_i (s; \theta) + \pi_i (s)) R_i (s) ds.
% \]
% where~$N_i (t)$ is the counting process with jumps at all~$t \in \bfT_i \cup \bfD_i$. Asymptotic consistency is guaranteed~\cite[Theorem VI.1.1]{Andersen1993} if
% \begin{equation}
% \label{eq:andersen1}
% n^{-1} \tilde U_n (\theta_0 ) \overset{P}{\to} 0,
% \end{equation}
% and
% \begin{equation}
% \label{eq:andersen2}
% n^{-1} \frac{d}{d \theta^{\top}} \tilde U_n (\theta) \big |_{\theta =
%   \theta_0} = \Xi (\theta),
% \end{equation}
% and
% \begin{equation}
% \label{eq:andersen3}
% \lim_{n \to \infty} P \left( \left | n^{-1} \frac{d^2}{d \theta_j d
%       \theta_k} \tilde U_n (\theta) \right | < M \text{ for all }
%   j,k \text{ and all } \theta \in \Theta_0 \right) = 1
% \end{equation}
% To prove~\eqref{eq:andersen1}, we decompose~$\tilde U_n (\theta_0)$ into
% three terms
% \begin{equation}
% \label{eq:decomp}
% n^{-1} \tilde U_n (\theta_0) = n^{-1} U_n (\theta_0 )  + n^{-1} \left(
%   \hat U_n (\theta_0) - U_n (\theta) \right) + n^{-1} \left(\tilde U_n
%   (\theta_0) - \hat U_n (\theta_0) \right)
% \end{equation}
% where, recall,~$\hat U_n (\theta_0)$ are the logistic score equations with $\int_0^\infty X_i(t,s) \beta(s) ds$ and~$\tilde U_n (\theta_0)$ with the approximation~$C_{i,t}^\top J_{\phi, \psi} {\bf b}$. \cite{Andersen1993} (Theorem VI.1.1) show that~$n^{-1} U_n (\theta_0)
% \to 0$. The second term
% \begin{align*}
% n^{-1} \left( \hat U_n (\theta_0) - U_n (\theta_0) \right) =
%   \frac{1}{n} \sum_{i=1}^n \int_0^{\tau} \frac{h^{(1)} (s;
%   \theta_0)}{\pi_i (s) + h (s;\theta_0)} d M_i (s).
% \end{align*}
% where~$h(\cdot; \theta_0)$ is given by~\eqref{eq:hazardlinear}. Lenglart's inequality implies the second term converges in probability to zero under Assumptions~\ref{E1} and~\ref{E2}. The third term satisfies
% \begin{align*}
%   &n^{-1} \left \| \hat U_n (\theta_0) - \tilde U_n (\theta_0) \right \| \\
%   \leq & M n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i} \bigg \| g
%          \left( \tilde W_{i,t}^\top \theta  + \sum_{k=K_x+1}^\infty \hat
%          c_{i,k} (t) \int_{t-\Delta}^t \hat \psi_k (s) \phi (s)^\top b
%          + \log (\pi_i (t) ) \right) - g \left( \tilde W_{i,t}^\top
%          \theta + \log (\pi_i (t)) \right) \bigg \| \\
% &\leq M n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
%     \sup_{x \in \mathbb{R}} \left \| g^\prime \left( x \right)
%   \right\| \times \left \| \sum_{k=K_x+1}^\infty \hat c_{i,k} (t)
%   \sum_{l=1}^{K_b} \int_{t-\Delta}^t \hat \psi_k (s) \phi_l (s) b_l
%   \right \| \\
% &= \frac{M}{4} n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
%   \sum_{l=1}^{K_b} \left \| \int_{t-\Delta}^t
%   \left( X(t,s) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \right)
%   \phi_l (s) b_l\right \| \\
% &\to \frac{M}{4} \int_0^\tau \sum_{l=1}^{K_b} \left \| \int_{t-\Delta}^t
%   \left( X(t,s) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \right)
%   \phi_l (s) b_l\right \| (f_0(t) + f_1(t)) dt
% \end{align*}
% where~$M = \sup \| \tilde W_{i,t} \|$,~$g(x) = 1/(1+\exp(-x))$ is the
% expit function.
% The second inequality is due to the Taylor remainder theorem. The third is due to~$g^\prime (x) = e^x/(1+e^x)^2 \leq e^0/(1+e^0)^2 = 1/4$, reordering the summation, and rewriting the error term in terms of the difference between~$X(t,s)$ and the approximation with truncation level~$K_x$. Letting~$n \to \infty$ allows us to re-write the outside sums in terms of the integrated difference where the integral is with respect to the joint event and sampling distributions~$(f_0(t) + f_1 (t))$. Finally, under Assumptions~\ref{assumption:truncation}, \cite{Park2018} show
% \[
% X(t,s) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \overset{P}{\to} 0
% \]
% as~$K_x \to \infty$, which implies the third term goes to zero as the truncation level goes to infinity. The same argument can be used in conjunction under assumptions~\ref{E1} and~\ref{E4} to prove~\eqref{eq:andersen2}.

% To prove~\eqref{eq:andersen3}, we start with equation~\eqref{eq:approxscore}, which we rewrite here for completeness:
% \[
% \hat{U}_n (\theta) = \sum_{i=1}^n \left[ \sum_{u \in \bfT_i} w_i(u; \theta)
%   \frac{h^{(1)} (u; \theta)}{ h ( u; \theta)}  - \sum_{u \in \bfD_i} w_i(u;
%   \theta) \frac{h_i^{(1)} (u; \theta)}{ \pi_i (u) } \right].
% \]
% Let~$N_i^{(e)} (t)$ and $N_i^{(s)} (t)$ be the event and subsampling counting processes with jumps at $t \in \bfT_i$ and $\bfD_i$ respectively.  Then
% \begin{equation}
% \label{eqapp:upperbound}
% \left | n^{-1} \frac{d^2}{d \theta_j d \theta_k} \tilde U_n (\theta)  \right | \leq \frac{1}{n} \sum_{i=1}^n \int_0^\tau w_i (t;\theta) \times H_{in} (t) R_i (t) dN_i^{(e)} (t) +
% \frac{1}{n} \sum_{i=1}^n \int_0^\tau \frac{w_i (t;\theta)}{\pi_i (t)} \times G_{in} (t) R_i (t) dN_i^{(e)} (t)
% \end{equation}
% where $H_{in}(t)$ and $G_{in}(t)$ are from Condition VI.1.1(E) in~\cite[pp. 421]{Andersen1993}. The first term converges in probability to a finite quantity by~\cite{Andersen1993}.  Since~$w_i(t;\theta)/\pi_i (t) = (\pi_i(t)+h_i(t;\theta))^{-1}$, the second term which simplifies to
% \[
% \frac{1}{n} \sum_{i=1}^n \int_0^\tau \frac{G_{in} (t)}{\pi_i (t)+h_i(t;\theta)} R_i(t) dN_i^{(e)} (t)
% \leq
% \frac{1}{L \cdot n} \sum_{i=1}^n \int_0^\tau G_{in} (t) R_i (t) dN_i^{(e)} (t)
% \]
% by Assumption~\ref{E1} (i.e., the subsampling rate is lower bounded by $L$). The right hand side is the optional variation of the local square integrable martingale
% $$
% \frac{1}{L \cdot n} \sum_{i=1}^n \int_0^t G^{1/2}_{in} (s) dN_i^{(e)} (s)
% $$
% This martingale has predicable variation process
% $$
% \frac{1}{L \cdot n} \sum_{i=1}^n \int_0^t G_{in} (s) \pi_i (s) R_i (s) ds
% $$
% Since both processes have the same limits, conditions VI.1.1(E) in~\cite{Andersen1993} and Assumption~\ref{E1} imply that the second term on the right hand side of~\eqref{eqapp:upperbound} also converges to a finite quantity as $n \to \infty$ for every $K_x$ which completes the proof.

% This proves~$\hat \theta_n \overset{P}{\to} \theta_0$ as $n \to \infty$ and $K_x \to \infty$. Note that the argument holds for any choice of weight functions~$w_i (t;\theta)$; implying convergence holds more broadly for all approximate score equations in~\eqref{eq:approxscore}.
% \end{proof}

% \begin{proof}[Proof of Asymptotic Normality]
% Consider a Taylor-expansion of $\tilde U_n (\theta)$ centered at $\theta_0$ when $\hat \theta_n \in \Theta_0$.  We can write as
% \begin{align*}
% \tilde U_n (\hat \theta_n) &= \tilde U_n (\theta_0) -  (\hat \theta_n - \theta_0) \frac{\partial}{\partial \theta} \tilde U_n (\theta) \mid_{\theta=\theta_0} - (\hat \theta_n - \theta_0) \sum_{l=1}^p (\hat \theta_{ln} - \theta_{l0}) \frac{\partial^2}{\partial \theta \partial \theta_l} \tilde U_n (\theta) \mid_{\theta=\theta^\star} \\
% 0 &= \tilde U_n (\theta_0) + (\hat \theta_n - \theta_0) \left[ \frac{\partial}{\partial \theta} \tilde U_n (\theta) \mid_{\theta=\theta_0} + \frac{1}{2} \sum_{l=1}^p (\hat \theta_{ln} - \theta_{l0}) \frac{\partial^2}{\partial \theta \partial \theta_l} \tilde U_n (\theta) \mid_{\theta=\theta^\star} \right] \\
% n^{1/2} (\hat \theta_n - \theta_0) &= \left[ \frac{1}{n} \frac{\partial}{\partial \theta} \tilde U_n (\theta) \mid_{\theta=\theta_0} + \frac{1}{2n} \sum_{l=1}^p (\hat \theta_{ln} - \theta_{l0}) \frac{\partial^2}{\partial \theta \partial \theta_l} \tilde U_n (\theta) \mid_{\theta=\theta^\star} \right]^{-1} n^{-1/2} \tilde U_n (\theta_0)
% \end{align*}
% where~$\theta^\star$ is on the line segment between $\hat \theta_n$ and $\theta_0$. First, the term
% $$
% \frac{1}{n} \frac{\partial}{\partial \theta} \tilde U_n (\theta) \mid_{\theta=\theta_0} + \frac{1}{2n} \sum_{l=1}^p (\hat \theta_{ln} - \theta_{l0}) \frac{\partial^2}{\partial \theta \partial \theta_l} \tilde U_n (\theta) \mid_{\theta=\theta^\star}
% \overset{P}{\to} \Xi(\theta_0)
% $$
% under conditions VI.1.1(A)--(E) in~\cite{Andersen1993} and Assumptions~\ref{E1}--\ref{E4}.  To see this, note the first term converges to $\Xi(\theta_0)$ while the second term is bounded in probability by $p M \| \theta^\star - \theta_0 \|$ for some finite constant~$M$ independent of~$\theta^\star$ where $\| \cdot \|$ is the Euclidean norm.  The second term therefore goes to zero since $\| \theta^\star - \theta_0 \| \to 0$ as $n \to \infty$.

% We now consider $n^{-1/2} \tilde U_n (\theta_0 )$. Recall $\tilde U_n (\theta_0)$ can be decomposed into three terms as in~\eqref{eq:decomp}. Here, we assume $K_x \to \infty$ so the final term is negligible.  This leaves two terms
% $$
% U_n (\theta_0) = \sum_{i=1}^n \int_0^\tau \frac{h^{(1)}(u; \theta)}{h (u;\theta)} dM_i^{(e)} (t)
% $$
% where~$N_i^{(e)} (t)$ and $N_i^{(s)} (t)$ are the orthogonal event and subsampling counting processes with jumps at times $t \in \bfT_i$ and $t \in \bfD_i$ respectively.
% and
% \begin{align*}
% (\hat U_n (\theta_0) - U_n (\theta_0) )
% &= \sum_{i=1}^n \int_0^\tau \frac{h^{(1)}(s; \theta_0)}{\pi_i (s) + h(s; \theta_0)} dM_i (s) \\
% &= \sum_{i=1}^n \int_0^\tau \frac{h^{(1)}(s; \theta_0)}{\pi_i (s) + h(s; \theta_0)} dM^{(e)}_i (s) +
% \sum_{i=1}^n \int_0^\tau \frac{h^{(1)}(s; \theta_0)}{\pi_i (s) + h(s; \theta_0)} dM_i^{(s)} (s) \\
% &= \sum_{i=1}^n \int_0^\tau (1-w(s;\theta_0)) \cdot \frac{h^{(1)}(s; \theta_0)}{h_i (s;\theta_0)} dM_i^{(e)} (s) +
% \sum_{i=1}^n \int_0^\tau w(s;\theta_0) \cdot \frac{h^{(1)}(s; \theta_0)}{\pi_i (s)} dM_i^{(s)} (s)
% \end{align*}
% Taking difference with $U_n(\theta_0)$, the first term becomes
% \[
% \sum_{i=1}^n \int_0^\tau w(s;\theta_0) \cdot \frac{h^{(1)}(s; \theta_0)}{h_i (s;\theta_0)} dM_i^{(e)} (s)
% \]
